Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique

### 2018-04-20 inst/rmd/paper.tex
changes

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

@@

\begin{figure}[h]

{\centering \includegraphics{figures/unnamed-chunk-13-1}

@@

\caption{(i) Mozambique in Africa, (ii) Districts of Mozambique with Manhiça highlighted in red, (iii) District of Manhiça with Maragra highlighted in red, (iv) Maragra SA with surrounding fields and village}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{figures/unnamed-chunk-15-1}

@@

\caption{i. Fumigation activities carried out by Maragra Malaria Control during study period, ii. Distribution of average time between sprayings of households}\label{fig:unnamed-chunk-15}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{figures/unnamed-chunk-18-1}

\caption{Age distribution by sex and worker status}\label{fig:unnamed-chunk-18}
\end{figure}

\begin{figure}[h]

@@

\caption{i. Monthly total precipitation in the Maniça district; ii. Average monthly temperature (bars) during the study period, as well as monthly maximum (red) and minimum (blue) temperatures}\label{fig:unnamed-chunk-19}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-20-1.pdf}
\caption{Clinical malaria (district of Manhiça), all-cause absenteeism
among Maragra workers, sick absenteeism among Maragra workers, positive
cases at company clinic, and test positivity rate at company clinic}
\end{figure}

@@

\begin{figure}[h]

{\centering \includegraphics{figures/unnamed-chunk-25-1}

@@

\caption{Rainfall and absenteeism: association of any rainfall with absenteeism rate (left) and association of rainfall amount and absenteeism (right)}\label{fig:unnamed-chunk-25}
\end{figure}

@@

\textbf{Effect of IRS on absenteeism}: Immediately following IRS, a
worker's likelihood of absence drops significantly (figure x, panel i).
As one would expect if the mechanism by which IRS reduces absence is
through reduced malaria infection, the effect of IRS during the low
transmission season is significant, but far less substantial in effect
size (figure x, panel ii).

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-26-1.pdf}
\caption{i. Absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

@@

The model results for sickness only absenteeism suggest that IRS has a
significant effect on permanent field workers. The effect is
directionally similar among temporary fieldworkers (but does not reach
the level of significance). Among non-fieldworkers, the effect of IRS is
mixed.

@@

\subsection{Externalities}\label{externalities}

@@

To check for this, we estimate the odds of absenteeism as a function of
receiving IRS \emph{during the 10 day period prior to receiving IRS}. If
IRS application is indeed endogenous, we would expect absenteeism to be
elevated during this period (since the increase in absenteeism would be
theoretically responsible for the application of IRS), a situation which
would require further statistical adjustment. If, on the other hand,
there is no endogeneity, we would expect absenteeism in the 10 day
period prior to IRS administration to be similar to other pre-IRS
absenteeism (adjusting for seasonality).

What follows are several variations of a model to assess whether IRS
application predicts pre-IRS absenteeism. In the final version of the
paper, we'll use whichever model is most appropriate, but this is left
here for discussion purposes. I've also included the code, so as to
inform the discussion. In the below models, \texttt{pre\_irs} refers to
the 10 day period prior to IRS administration. The models estimate the
odds of absence (ie, the estimates and confidence intervals are in the
form of odds ratios).

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ro_data <-}\StringTok{ }\NormalTok{ab_panel }\OperatorTok{%>%}\StringTok{ }\KeywordTok{left_join}\NormalTok{(irs, }\DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"date"}\NormalTok{, }\StringTok{"unidade"}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(days_since }\OperatorTok{<}\StringTok{ }
\StringTok{    }\DecValTok{0}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{pre_irs =} \KeywordTok{between}\NormalTok{(days_since, }\OperatorTok{-}\DecValTok{10}\NormalTok{, }\OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }\CommentTok{# mutate(time_period = lendable::time_period_extract(date)) %>%}
\CommentTok{# mutate(time_period = as.character(time_period)) %>%}
\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{time_period =} \KeywordTok{make_season}\NormalTok{(}\DataTypeTok{date =}\NormalTok{ date)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{absent_sick =} \KeywordTok{ifelse}\NormalTok{(}\KeywordTok{is.na}\NormalTok{(absent_sick), }
    \OtherTok{FALSE}\NormalTok{, absent_sick)) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{left_join}\NormalTok{(workers }\OperatorTok{%>%}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{select}\NormalTok{(oracle_number, }
\NormalTok{    sex, department, permanent_or_temporary), }\DataTypeTok{by =} \StringTok{"oracle_number"}\NormalTok{)}

\NormalTok{make_model <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{formula =} \StringTok{"absent ~ pre_irs + time_period"}\NormalTok{) \{}
\NormalTok{    ro_model <-}\StringTok{ }\KeywordTok{glm}\NormalTok{(}\KeywordTok{as.formula}\NormalTok{(formula), }\DataTypeTok{data =}\NormalTok{ ro_data, }\DataTypeTok{family =} \KeywordTok{binomial}\NormalTok{(}\StringTok{"logit"}\NormalTok{))}
\NormalTok{    coefs <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(}\KeywordTok{coef}\NormalTok{(ro_model))}
\NormalTok{    ci <-}\StringTok{ }\KeywordTok{confint}\NormalTok{(ro_model)}
\NormalTok{    ci <-}\StringTok{ }\KeywordTok{exp}\NormalTok{(ci)}
\NormalTok{    out <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{Variable =} \KeywordTok{names}\NormalTok{(coefs), }\DataTypeTok{Estimate =}\NormalTok{ coefs, }\DataTypeTok{Lower =}\NormalTok{ ci[, }
        \DecValTok{1}\NormalTok{], }\DataTypeTok{Upper =}\NormalTok{ ci[, }\DecValTok{2}\NormalTok{])}
    \KeywordTok{row.names}\NormalTok{(out) <-}\StringTok{ }\OtherTok{NULL}
\NormalTok{    out}\OperatorTok{$}\StringTok{`}\DataTypeTok{P value}\StringTok{`}\NormalTok{ <-}\StringTok{ }\KeywordTok{coef}\NormalTok{(}\KeywordTok{summary}\NormalTok{(ro_model))[, }\DecValTok{4}\NormalTok{]}
\NormalTok{    out}\OperatorTok{$}\NormalTok{Significant <-}\StringTok{ }\KeywordTok{ifelse}\NormalTok{(out}\OperatorTok{$}\StringTok{`}\DataTypeTok{P value}\StringTok{`} \OperatorTok{<=}\StringTok{ }\FloatTok{0.001}\NormalTok{, }\StringTok{"xxx"}\NormalTok{, }\KeywordTok{ifelse}\NormalTok{(out}\OperatorTok{$}\StringTok{`}\DataTypeTok{P value}\StringTok{`} \OperatorTok{<=}\StringTok{ }
\StringTok{        }\FloatTok{0.01}\NormalTok{, }\StringTok{"xx"}\NormalTok{, }\KeywordTok{ifelse}\NormalTok{(out}\OperatorTok{$}\StringTok{`}\DataTypeTok{P value}\StringTok{`} \OperatorTok{<=}\StringTok{ }\FloatTok{0.05}\NormalTok{, }\StringTok{"x"}\NormalTok{, }\StringTok{""}\NormalTok{)))}
    \KeywordTok{return}\NormalTok{(}\KeywordTok{kable}\NormalTok{(out, }\DataTypeTok{format =} \StringTok{"latex"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{kable_styling}\NormalTok{() }\OperatorTok{%>%}\StringTok{ }\KeywordTok{row_spec}\NormalTok{(}\DataTypeTok{row =} \KeywordTok{which}\NormalTok{(}\KeywordTok{grepl}\NormalTok{(}\StringTok{"pre_irs"}\NormalTok{, }
\NormalTok{        out}\OperatorTok{$}\NormalTok{Variable)), }\DataTypeTok{background =} \StringTok{"yellow"}\NormalTok{))}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# BASIC FORMULA}
\KeywordTok{make_model}\NormalTok{(}\StringTok{"absent ~ pre_irs + time_period"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H]
\centering
\begin{tabular}{l|r|r|r|r|l}
\hline
Variable & Estimate & Lower & Upper & P value & Significant\\
\hline
(Intercept) & 0.0498463 & 0.0474720 & 0.0523031 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE & 0.8050236 & 0.7002405 & 0.9211332 & 0.0019204 & xx\\
\hline
time\_periodMalaria season & 3.1215538 & 2.9408258 & 3.3145230 & 0.0000000 & xxx\\
\hline
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# BASIC FORMULA WITH INTERACTIONS}
\KeywordTok{make_model}\NormalTok{(}\StringTok{"absent ~ pre_irs*time_period"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H]
\centering
\begin{tabular}{l|r|r|r|r|l}
\hline
Variable & Estimate & Lower & Upper & P value & Significant\\
\hline
(Intercept) & 0.0496594 & 0.0472551 & 0.0521477 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE & 0.8741393 & 0.6918180 & 1.0889051 & 0.2443527\\
\hline
time\_periodMalaria season & 3.1397591 & 2.9537482 & 3.3386865 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE:time\_periodMalaria season & 0.8804465 & 0.6645722 & 1.1740347 & 0.3797816\\
\hline
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# BASIC FORMULA WITH INTERACTIONS AND ADJUSTING FOR SEX}
\KeywordTok{make_model}\NormalTok{(}\StringTok{"absent ~ pre_irs*time_period + sex"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H]
\centering
\begin{tabular}{l|r|r|r|r|l}
\hline
Variable & Estimate & Lower & Upper & P value & Significant\\
\hline
(Intercept) & 0.0350661 & 0.0325983 & 0.0376818 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE & 0.8880020 & 0.7026608 & 1.1064043 & 0.3043502\\
\hline
time\_periodMalaria season & 3.1716504 & 2.9834194 & 3.3729726 & 0.0000000 & xxx\\
\hline
sexM & 1.5960091 & 1.4919474 & 1.7085243 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE:time\_periodMalaria season & 0.8579023 & 0.6473160 & 1.1443754 & 0.2910119\\
\hline
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# BASIC FORMULA WITH INTERACTIONS AND ADJUSTING FOR SEX AND DEPARTMENT}
\KeywordTok{make_model}\NormalTok{(}\StringTok{"absent ~ pre_irs*time_period + sex + department"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H]
\centering
\begin{tabular}{l|r|r|r|r|l}
\hline
Variable & Estimate & Lower & Upper & P value & Significant\\
\hline
(Intercept) & 0.0564718 & 0.0510602 & 0.0623971 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE & 0.9242121 & 0.7310398 & 1.1520107 & 0.4962745\\
\hline
time\_periodMalaria season & 3.1302404 & 2.9439618 & 3.3294967 & 0.0000000 & xxx\\
\hline
sexM & 1.1923874 & 1.1059966 & 1.2861150 & 0.0000048 & xxx\\
\hline
departmentFactory & 1.0828452 & 1.0009732 & 1.1717926 & 0.0476615 & x\\
\hline
departmentField & 0.5767584 & 0.5330008 & 0.6243185 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE:time\_periodMalaria season & 0.8145012 & 0.6141075 & 1.0872550 & 0.1585481\\
\hline
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# BASIC FORMULA WITH INTERACTIONS AND ADJUSTING FOR SEX AND DEPARTMENT AND}
\CommentTok{# STATUS}
\KeywordTok{make_model}\NormalTok{(}\StringTok{"absent ~ pre_irs*time_period + sex + department + permanent_or_temporary"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H]
\centering
\begin{tabular}{l|r|r|r|r|l}
\hline
Variable & Estimate & Lower & Upper & P value & Significant\\
\hline
(Intercept) & 0.0617511 & 0.0558057 & 0.0682626 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE & 1.0466179 & 0.8252949 & 1.3092306 & 0.6983498\\
\hline
time\_periodMalaria season & 2.9528835 & 2.7744446 & 3.1438877 & 0.0000000 & xxx\\
\hline
sexM & 1.2300194 & 1.1386295 & 1.3293865 & 0.0000002 & xxx\\
\hline
departmentFactory & 1.0837360 & 1.0014970 & 1.1731018 & 0.0462328 & x\\
\hline
departmentField & 1.3324160 & 1.2272323 & 1.4470610 & 0.0000000 & xxx\\
\hline
permanent\_or\_temporaryTemporary & 0.0839961 & 0.0744587 & 0.0944456 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  pre\_irsTRUE:time\_periodMalaria season & 0.6682310 & 0.5016567 & 0.8956885 & 0.0063480 & xx\\
\hline
\end{tabular}
\end{table}

@@

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{float}
\floatplacement{figure}{H}

@@

\begin{figure}[!h]

{\centering \includegraphics{figures/unnamed-chunk-14-1}

@@

\caption{(i) Mozambique in Africa, (ii) Districts of Mozambique with Manhiça highlighted in red, (iii) District of Manhiça with Maragra highlighted in red, (iv) Maragra SA with surrounding fields and village}\label{fig:unnamed-chunk-14}
\end{figure}

@@

\begin{figure}[!h]

{\centering \includegraphics{figures/unnamed-chunk-16-1}

@@

\caption{i. Fumigation activities carried out by Maragra Malaria Control during study period, ii. Distribution of average time between sprayings of households}\label{fig:unnamed-chunk-16}
\end{figure}

@@

\begin{figure}[!h]

@@

\caption{Age distribution by sex and worker status}\label{fig:unnamed-chunk-19}
\end{figure}

\begin{figure}[!h]

{\centering \includegraphics{figures/unnamed-chunk-20-1}

\caption{i. Monthly total precipitation in the Maniça district; ii. Average monthly temperature (bars) during the study period, as well as monthly maximum (red) and minimum (blue) temperatures}\label{fig:unnamed-chunk-20}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-21-1.pdf}
\caption{Clinical malaria (district of Manhiça), all-cause absenteeism
among Maragra workers, sick absenteeism among Maragra workers, positive
cases at company clinic, and test positivity rate at company clinic}
\end{figure}

@@

\begin{figure}[!h]

{\centering \includegraphics{figures/unnamed-chunk-26-1}

@@

\caption{Rainfall and absenteeism: association of any rainfall with absenteeism rate (left) and association of rainfall amount and absenteeism (right)}\label{fig:unnamed-chunk-26}
\end{figure}

@@

\subsection{Analysis}\label{analysis}

\subsubsection{Effect of IRS on
absenteeism}\label{effect-of-irs-on-absenteeism}

Immediately following IRS, a worker's likelihood of absence drops
significantly (appendix figure, panel A). As one would expect if the
mechanism by which IRS reduces absence is through reduced malaria
infection, the effect of IRS during the low transmission season is
significant, but far less substantial in effect size (appendix figure,
panel B).

@@

The model results for sickness only absenteeism (table 5) suggest that
IRS has a significant effect on permanent field workers. The effect is
directionally similar among temporary fieldworkers (but does not reach
the level of significance). Among non-fieldworkers, the effect of IRS is
mixed.

@@

\subsubsection{Externalities}\label{externalities}

@@

To check for this, we estimate the odds of absenteeism as a function of
receiving IRS \emph{during the 10 day period prior to receiving IRS}. If
IRS application is indeed endogenous, we would expect absenteeism to be
elevated during this period (since the increase in absenteeism would be
theoretically responsible for the application of IRS), a situation which
would require further statistical adjustment. If, on the other hand,
there is no endogeneity, we would expect absenteeism in the 10 day
period prior to IRS administration to be similar to other pre-IRS
absenteeism (adjusting for
seasonality).\todo{Should add model specification formula here.}

The below shows our robustness check for all cause absenteeism.

\begin{table}[H]
\centering
\begin{tabular}{l|r|r|r|r|l}
\hline
Variable & Estimate & Lower & Upper & P value & Significant\\
\hline
(Intercept) & 0.0661899 & 0.0614958 & 0.0711710 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  10 days prior to IRS & 0.9229176 & 0.7300243 & 1.1503819 & 0.4886243\\
\hline
Malaria season & 3.1173457 & 2.9319429 & 3.3156586 & 0.0000000 & xxx\\
\hline
departmentFactory & 1.0944261 & 1.0118141 & 1.1841680 & 0.0245210 & x\\
\hline
departmentField & 0.5426841 & 0.5036184 & 0.5850353 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  10 days prior to IRS:Malaria season & 0.8172244 & 0.6161822 & 1.0908542 & 0.1653822\\
\hline
\end{tabular}
\end{table}

The below shows our robustness check for sick only absenteeism. Unlike
with all cause absenteeism, during malaria season, being in the period
10 days prior to IRS is associated with statistically greater likelihood
of being absent for illness. In other words, it appears that there is
somewhat of a feedback loop: when a worker misses work due to illness,
his/her likelihood of getting IRS doubles in the next 10
days.\todo{What to do about this???}

\begin{table}[H]
\centering
\begin{tabular}{l|r|r|r|r|l}
\hline
Variable & Estimate & Lower & Upper & P value & Significant\\
\hline
(Intercept) & 0.0098162 & 0.0079914 & 0.0119339 & 0.0000000 & xxx\\
\hline
\rowcolor{yellow}  10 days prior to IRS & 0.6780540 & 0.3484288 & 1.1791509 & 0.2069281\\
\hline
Malaria season & 1.1637020 & 0.9827900 & 1.3767569 & 0.0777162 & \\
\hline
departmentFactory & 1.3068546 & 1.0428447 & 1.6460818 & 0.0214002 & x\\
\hline
departmentField & 0.6713828 & 0.5396839 & 0.8403182 & 0.0004142 & xxx\\
\hline
\rowcolor{yellow}  10 days prior to IRS:Malaria season & 2.2225088 & 1.0747201 & 4.8587934 & 0.0360020 & x\\
\hline
\end{tabular}
\end{table}

@@

\section{Appendix}\label{appendix}

\subsection{Unadjusted absenteeism by time since
IRS}\label{unadjusted-absenteeism-by-time-since-irs}

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-33-1.pdf}
\caption{i. Absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

\subsection{Unadjusted sick absenteeism by time since
IRS}\label{unadjusted-sick-absenteeism-by-time-since-irs}

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-34-1.pdf}
\caption{i. Sick absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}
